\forestclaw: Hybrid forest-of-octrees AMR for hyperbolic conservation laws

### 2013-07-31 docs/parco13/paper.tex
Comment on latest weak scaling results

\begin{figure}
\begin{center}
  \includegraphics[angle=-90,width=.8\columnwidth]{pdf/uni_advance_strong-crop}
  \\[1ex]
  \includegraphics[angle=-90,width=.8\columnwidth]{pdf/uni_exchange_strong-crop}
\end{center}
\caption{Strong scaling of MPI parallelism for advection on a uniform mesh.
  Top: run time of time integration.  Bottom: time spent in local and parallel
  neighbor exchanges.  The number of patches is $2^{2 \ell}$ at level $\ell$.
  The flat lines for the smaller runs are caused by having
  less patches than MPI processes, leaving some of them idle.  For each data point
  we use the maximum time required across all processes.}
\label{fig:uniscale}
\end{figure}%
We begin our analysis of Example 1 with uniform-mesh experiments run on TACC's
\emph{Stampede} supercomputer at different levels of resolution.  First of all,
we use 1 to 16 MPI processes on one 16-core compute node, obtaining a strong
scaling efficiency for the time integration between 97\%--103\% depending on
the resolution (from levels 1 and 8).  Then, we examine processor counts from
16 to 256 using 16 cores per node.  The scaling behavior remains linear for
the time integration itself, and mostly linear for the local and parallel
neighbor exchanges which require about 10\% of the time integration run time;
see \Fig{uniscale}.  Due to space constraints we omit the
corresponding weak scaling results, which are nearly optimal as well.

>>>>

\begin{figure}
\begin{center}
  \includegraphics[angle=-90,width=.8\columnwidth]{pdf/uni_advance_strong-crop}
  \\[1ex]
  \includegraphics[angle=-90,width=.8\columnwidth]{pdf/uni_exchange_strong-crop}
\end{center}
\caption{Strong scaling of MPI parallelism for advection on a uniform mesh.
  Top: run time of time integration.  Bottom: time spent in local and parallel
  neighbor exchanges.  The number of patches is $2^{2 \ell}$ at level $\ell$.
  The flat lines for the smaller runs are caused by having
  less patches than MPI processes, leaving some of them idle.  For each data point
  we use the maximum time required across all processes.}
\label{fig:uniscale}
\end{figure}%
We begin our analysis of Example 1 with uniform-mesh experiments run on TACC's
\emph{Stampede} supercomputer at different levels of resolution.  First of all,
we use 1 to 16 MPI processes on one 16-core compute node, obtaining a strong
scaling efficiency for the time integration between 97\%--103\% depending on
the resolution (from levels 1 and 8).  Then, we examine processor counts from
16 to 256 using 16 cores per node.  The scaling behavior remains linear for
the time integration itself, and mostly linear for the local and parallel
neighbor exchanges which require about 10\% of the time integration run time;
see \Fig{uniscale}.

We have examined weak scalability as well by using four times as many processes
for each level inclease, from level 6 at 64 cores to level 10 at 4096.  The
exchange times stay consistently below 16\% of the time integration.  The time
in seconds per time integration step varies between .0578 and .0602,
which yields a parallel efficiency of 96\%.
